---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r, echo=TRUE}
require(data.table)
require(dplyr)
```
## Loading and preprocessing the data
```{r, echo=FALSE}
data <- fread('activity.csv')
```

## What is mean total number of steps taken per day?

###1. Calculate the total number of steps taken per day:
```{r, echo=TRUE}
spd <- na.omit(data) %>% group_by(date) %>% summarise(n=sum(steps))
spd
```

###2. Make a histogram of the total number of steps taken each day
```{r, echo=TRUE}
hist(spd$n,main="Steps taken per day",xlab="steps",col="darkgreen")
```

###3. Calculate and report the mean and median of the total number of steps taken per day
```{r, echo=TRUE}
mean_spd <- mean(spd$n,na.rm=TRUE)
median_spd <- median(spd$n,na.rm=TRUE)
options(scipen=1, digits=2)
```

The mean of the total number of steps taken per day is **`r mean_spd`**.

The median of the total number of steps taken per day is **`r median_spd`**.

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
